Pillar 1 - Sequential Pattern Mining

### 2019-01-29 Pillar 1 - Sequential Pattern Mining.Rmd
Deleting experiments

    item_PF = paste(`Course ID`, PF, sep = "_"),
    item_HL = paste(`Course ID`, HL, sep = "_")
    ) %>%
  rename(
    item = `Course ID`
  )
```
### SOFIA---Take not take courses
```{r}
#item and sequenceID

d_transactions_tmp <- expand.grid(sequenceID = unique(d_transactions$sequenceID),item = unique(d_transactions$item)) %>%
  left_join(d_transactions, by = c("sequenceID","item")) %>%
  mutate(
    Taken= case_when(
     is.na(Grade)  ~ "not taken",
      T             ~ "taken"),
    item_Taken= paste(item,Taken, sep = "_")
     )

@@

##Not ready to move up:
##Puting students into take and not take. 
```{r}
#This df has 731,676 rows:
test <- expand.grid(`Student ID`= unique(d_transcript$`Student ID`),`Course ID`= unique(d_course$`Course ID`)) %>%
  left_join(d_transcript, by=c("Course ID", "Student ID")) %>%
  filter(
     Type != "Mandatory",                  # (i) mandatory courses e.g. COR, CAP, etc
    ! Letters %in% c("SKI", "PRO",        # (ii) skills & projects (taken by majority of students)
                     "SAS", "SAH", "SAC") # (iii) courses of semester abroad (uninformative)
  )%>%
  select(`Course ID`, `Student ID`, Grade, Year_numerical, Period) %>%
  mutate(
    take_course = case_when(
      is.na(Grade)  ~ "not taken",
      T             ~ "taken"
      ),
     PFN = case_when(
       is.na(Grade)  ~ "not",
       Grade >= 5.5  ~ "pass",
       Grade < 5.5   ~ "fail"
       ),
    Item = paste(`Course ID`, take_course, sep="_")
    )

```{r}
trans <- test %>%
 mutate(
    Period  = substr(Period, 1, 1),
    eventID = as.numeric(paste(Year_numerical, Period, sep = ""))
    ) %>%
   rename(sequenceID = `Student ID`)%>%
  select(sequenceID, eventID, Item) %>%
  make_transaction(item=Item)

```{r}
# Run the apriori algorithm with desired parameters
my_apriori <- function(data, appearance = NULL){

  data %>%
    apriori(
      parameter = list(
        supp = 0,    # min support
        smax = 1,    # max support
        conf = 0,    # min confidence
        minlen = 2,  # min length of 
        maxlen = 2,  # max length of rule
        ext = TRUE,
        arem = "diff",
        aval = TRUE,
        minval = 0
        ),
      appearance = appearance,
      control = list(
        verbose = FALSE
        )
      ) #%>%
    #clean_AR

#
# Generating asocciation rules
AR <- my_apriori(trans)

AR %>%
    as("data.frame") %>%
    filter(
      count >= 1
    )

```
```

>>>>

    item_PF = paste(`Course ID`, PF, sep = "_"),
    item_HL = paste(`Course ID`, HL, sep = "_")
    ) %>%
  rename(
    item = `Course ID`
  )
```
### Adding not taken courses
```{r}
d_transactions_tmp <- expand.grid(sequenceID = unique(d_transactions$sequenceID),item = unique(d_transactions$item)) %>%
  left_join(d_transactions, by = c("sequenceID","item")) %>%
  mutate(
    Taken= case_when(
     is.na(Grade)  ~ "not taken",
      T             ~ "taken"),
    item_Taken= paste(item,Taken, sep = "_")
     )

@@

##Not ready to move up:
